\begin{thebibliography}{10}
\bibitem{mott72} Mott, N. F.; Peierls, R. (1937). "Discussion of the paper by de Boer and Verwey". Proceedings of the Physical Society 49 (4S): 72

\bibitem{efros75} A L Efros and B I Shklovskii , J. Phys. C8, L49 (1975)

\bibitem{glazman05} L.I. Glazman, M. Pustilnik, in "Nanophysics: Coherence and Transport," eds. H. Bouchiat et al. (Elsevier, 2005), pp. 427-478

\bibitem{kirkengen09} M. Kirkengen , J. Bergli, "Slow relaxation and equilibrium dynamics in a two-dimensional Coulomb glass: Demonstration of stretched exponential energy correlations" PHYSICAL REVIEW B 79, 075205 2009

\bibitem{aharony92} A. Aharony, Y. Zhang, M.P. Sarachik, "Universal Crossover in Variable Range Hopping with Coulomb Interactions", Physical Review Letters 1992

\bibitem{joung} D. Joungand, S. Khondaker, "Efros-Shklovskii variable range hopping in reduced graphene oxide sheets of varying carbon sp2 fraction", http://arxiv.org/pdf/1210.1876.pdf

\bibitem{glatz09} A. Glatz, I. Beloborodov, "Thermoelectric and Seebeck coefficients of granular metals", PHYSICAL REVIEW B 79, 235403 2009

\bibitem{chen} L. Chen, S. Gao, X. Zeng, A. Mehdizadeh Dehkordi,T. M. Tritt,and S. J. Poon, "Uncovering High Thermoelectric Figure of Merit in (Hf,Zr)NiSn Half-Heusler Alloys" , http://arxiv.org/pdf/1505.07773.pdf

\bibitem{ortuno04} M. Ortuno , A. Somoza, "Coulomb Glasses", http://www.lancaster.ac.uk/users/esqn/windsor04/docs/artuno-cg.pdf

\bibitem{beloborodov05} I. S. Beloborodov, A. V. Lopatin, F. W. J. Hekking, R. Fazio, and V. M. Vinokur , "Thermal transport in granular metals ",Europhys. Lett. 69, 435 (2005)

\bibitem{glatz08} A. Glatz ,I. S. Beloborodov , "Nanogranular Thermoelectrics" , http://arxiv.org/pdf/0810.5545.pdf

\bibitem{Gebhard03} B. Gebhard, "The Mott Metal-Insulator Transition: Models and Methods", Springer 2003

\bibitem{Glazman05} L. Glazman, M. Pustilnik, "Low-Temperature Transport Through A Quantum Dot", http://arxiv.org/pdf/cond-mat/0501007v2.pdf

\bibitem{Liu10} H. Liu, A. Pourret, P. Guyot-Sionnest, "Mott and Efros-Shklovskii Variable Range Hopping in CdSe Quantum Dots Films", ACS Nano, 2010, 4 (9), pp 5211-5216

\bibitem{Vinokur08} A. Glatz, V. Vinokur, J. Bergli, M. Kirkengen, Y. Galperin, "The Coulomb gap and low energy statistics for Coulomb glasses", Journal of Statistical Mechanics: Theory and Experiment, 2008

\bibitem{Kittel96} C. Kittel, "Introduction to Solid State Physics", Wiley, 1996

\bibitem{Beloborodov07} I. Beloborodov, A. Lopatin, V. Vinokur, K. Efetov, "Granular Electronic Systems", Reviews of Modern Physics, Volume 79, April-June 2007

\bibitem{Sadovskyy14} I. Sadovskyy, A. Koshelev, C. Phillips, D. Karpeev, A. Glatz, "Stable large-scale solver for Ginzburg-Landau equations for superconductors", Journal of Computational Physics, 09/2014

\bibitem{Ferrero14} E. Ferrero, A. Kolton, M. Palassini, "Parallel kinetic Monte Carlo simulation of Coulomb glasses" ,arXiv:1407.5026

\bibitem{Krauth06} W. Krauth, "Statistical Mechanics: Algorithms and Computations", Oxford University Press, Oxford, 2006, pp. 33–34

\bibitem{Newman99} M. Newman, G. Barkema, "Monte Carlo Methods in Statistical Physics", Oxford University Press, Oxford, 1999, pp. 41-42

\bibitem{Sparks16} T. Sparks, M. Gaultois, A. Oliynyk, J. Brgoch, B. Meredig, "Data mining our way to the next generation of thermoelectrics", Scripta Materialia, Volume 111, 15 January 2016, Pages 10–15

\bibitem{Chandra??} R. Chandra, "Mechanical vapour compression refrigeration", Refrigeration and Air Conditioning, New Delhi, India: PHI Learning. p. 3. ISBN 81-203-3915-0.

\bibitem{Brown63} J. Brown, "Thermodynamics of a Rubber Band", American Journal of Physics, 31 (5): 397–397, May 1963, doi:10.1119/1.1969535

\bibitem{Miszczak15} M. Miszczak, "GINZBURG-LANDAU SIMULATIONS OF NARROW SUPERCONDUCTING STRIPS" , Northern Illinois University, Department of Physics, 2015

\bibitem{Kittel96} C. Kittel, "Introduction to Solid State Physics", 7th Ed., Wiley, (1996)

\bibitem{Reichhardt10} O. Reichhardt, C. Reichhardt, "Commensurability, Jamming, and dynamics for vortices in funnel geometries" ,Physical Review B 81, 2010

\bibitem{Haag14} L. Haag, G. Zechner, W. Lang, M. Dosmailov, M. Bodea, J. Pedarnig "Strong vortex matching effects in YBCO films with periodic modulations of the superconducting order parameter fabricated by masked ion irradiation", Physica C: Superconductivity, Volume 503, 2014, pg 75-81

\bibitem{Horii15} S. Horii, M. Haruta, A. Ichinose, T. Doi, "Evidence for enhancement of vortex matching field above 5 T and oxygen-deficient annuli around barium-niobate nanorods", Journal of Applied Physics 118, 133907 (2015)

\bibitem{Rizzo16} F.Rizzo, A.Augieri, A. Armenio, V. Galluzzi, A. Mancini, V. Pinto, A. Rufoloni, A. Vannozzi, M. Bianchetti, A. Kursumovic, J. MacManus-Driscoll, A. Meledin, G. Van Tendeloo, G. Celentano, "Enhanced 77 K vortex-pinning in Y Ba2Cu3O7−x films with Ba2Y TaO6 and mixed Ba2Y TaO6 + Ba2Y NbO6 nano-columnar inclusions with irreversibility field to 11 T", APL Mater. 4, 061101 (2016); doi: 10.1063/1.4953436

\bibitem{Thakur09} A. Thakur, S. Ooi, S. Chockalingam, J. Jesudasan, P. Raychaudhuri, K. Hirata, "Vortex matching effect in engineered thin films of NbN", APPLIED PHYSICS LETTERS 94, 262501 2009

\bibitem{Sabatino10} P. Sabatino, C. Cirillo, G. Carapella, M. Trezza, and C. Attanasio, "High field vortex matching effects in superconducting Nb thin films with a nanometersized
square array of antidots", Journal of Applied Physics 108, 053906 (2010)

\bibitem{Lu06} Q. Lu, O. Reichhardt, C. Reichhardt, "Reversible vortex ratchet effects and ordering in superconductors with simple asymmetric potential arrays", PHYSICAL REVIEW B 75, 2007

\bibitem{Wambaugh99} J. Wambaugh, C. Reichhardt, C. Olson, F. Marchesoni , F. Nori, "Superconducting fluxon pumps and lenses", VOLUME 83, NUMBER 24 PHYSICAL REVIEW LETTERS, 1999

\bibitem{Yu10} K. Yu, M. Hesselberth, P. Kes, B. Plourde, "Vortex dynamics in superconducting channels with periodic constrictions", PHYSICAL REVIEW B 81, 2010

\bibitem{Berdiyorov06} G. Berdiyorov, M. Milošević, F. Peeters, "Vortex configurations and critical parameters in superconducting thin films containing antidot arrays: Nonlinear Ginzburg-Landau theory", PHYSICAL REVIEW B 74, 2006

\bibitem{Mott68} N. Mott, "Conduction in glasses containing transition metal ions", Cambridge, Journal of non-crystaline solids, 1968

\bibitem{Glazman05} L. Glazman, M. Pustilnik,"LOW-TEMPERATURE TRANSPORT THROUGH A QUANTUM DOT" arXiv:cond-mat/0501007 v2 10 Oct 2005

\bibitem{Tsigankov02} D. Tsigankov, A. Efros, "Variable Range Hopping in Two-Dimensional Systems of Interacting Electrons", VOLUME 88, NUMBER 17 PHYSICAL REVIEW LETTERS 2002

\bibitem{Young66} W. Young and E. Elcock,"Monte Carlo studies of vacancy migration in binary ordered alloys", Proceedings of the Physical Society 89 (1966) 735.

\bibitem{Serebrinsky11} S. Serebrinsky, "Physical time scale in kinetic Monte Carlo simulations of continuous-time Markov chains", PHYSICAL REVIEW E 83, (2011)

\bibitem{Abeles75} B. Abeles, P. Sheng, M. Coutts, Y. Arie, "Structural and electrical properties of granular metal films", Advances in Physics, 1975

\bibitem{Hubbard09} D. Hubbard, D. Samuelson, "Modeling Without Measurements". OR/MS: 28–33. 2009

\bibitem{Kalos08} M. Kalos, P. Whitlock, "Monte Carlo Methods", Wiley-Blackwell, 2008

\bibitem{Everitt02} B. Everitt, "The Cambridge Dictionary of Statistics", CUP. ISBN 0-521-81099-X, 2002

\bibitem{Dommelen13} L. van Dommelen, "A.11 Thermoelectric effects". Eng.fsu.edu. 2002-02-01. Retrieved 2013-04-22.

\bibitem{Kwok16} W. Kwok, U. Welp, A. Glatz1, A. Koshelev1, K. Kihlstrom1, G. Crabtree, "Vortices in high-performance high-temperature superconductors", Reports on Progress in Physics, 2016

\bibitem{Rowe05} D. Rowe, "Thermoelectrics Handbook: Macro to Nano.", CRC Press. ISBN 978-1-4200-3890-3., 2005

\end{thebibliography}
